Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-17 paper/main.tex
add subsection for top-level functions

When accessed (unless its value has been set to \texttt{None}), \texttt{davos.project} will return a \texttt{Project} object that represents the project used by the current notebook (strings assigned to \texttt{davos.project} are converted to \texttt{Project}s internally). 
This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
\texttt{Project}s can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects.

@@

% \subsubsection{Other top-level Davos functions}\label{subsec:toplevel}

>>>>

When accessed (unless its value has been set to \texttt{None}), \texttt{davos.project} will return a \texttt{Project} object that represents the project used by the current notebook (strings assigned to \texttt{davos.project} are converted to \texttt{Project}s internally). 
This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
\texttt{Project}s can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects (see Sec.~\ref{subsec:toplevel}).

@@

\subsubsection{Other top-level Davos functions}\label{subsec:toplevel}
\textcolor{red}{\textbf{TODO: add content}}
